Longitudinal Principal Manifold Estimation

### 2023-11-10 paper/main.tex
Updates from Overleaf

where $\mathcal{F}(\mathbb{P})$ is the collection of functions $f \in C(\mathbb{R}^{d} \to \mathbb{R}^{D})$ such that $\lim_{\|r\|_{\mathbb{R}^{d}} \to \infty}\|f(r)\|_{\mathbb{R}^{D}} = \infty$, the components of the function $f$ are in $\nabla^{-\otimes 2}L^2(\mathbb{R}^{d}) = \left\{u \in \mathcal{D}'(\mathbb{R}^{d}): \|\nabla^{\otimes 2} u\|_{\mathbb{R}^{d \times d}} \in L^2(\mathbb{R}^{d})\right\}$, and the projection function of $f$ satisfies the following equality $\sup_{x \in \text{supp}(\mathbb{P})}\|\pi_f(x)\|_{\mathbb{R}^{d}} = 1$. 

>>>>

where $\mathcal{F}(\mathbb{P})$ is the collection of functions $f \in C(\mathbb{R}^{d} \to \mathbb{R}^{D})$ such that $\lim_{\|r\|_{\mathbb{R}^{d}} \to \infty}\|f(r)\|_{\mathbb{R}^{D}} = \infty$, the components of the function $f$ are in $\nabla^{-\otimes 2}L^2(\mathbb{R}^{d}) = \left\{u \in \mathcal{D}'(\mathbb{R}^{d}): \|\nabla^{\otimes 2} u\|_{\mathbb{R}^{d \times d}} \in L^2(\mathbb{R}^{d})\right\}$, the set $\mathcal{D}'(\mathbb{R}^d)$ denotes the collection of generalized functions defined on $\mathbb{R}^d$ (also known as ``distributions" in the mathematical community, see Chapter 6 of \cite{rudin1991functional} for details), and the projection function of $f$ satisfies the following equality $\sup_{x \in \text{supp}(\mathbb{P})}\|\pi_f(x)\|_{\mathbb{R}^{d}} = 1$. 
